Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2016-02-05 manuscript/supplemental_material.Rnw
add contributors of samples to supplemental material

\begin{table}
  \begin{tabular}{c p{1.5in} c p{2in}}
    \toprule
    Species                       & Collector & Experiment Number & Sample Number(s) \\
    \midrule
    \textit{Ateles fusciceps}     &  & & \\
    \textit{Bos taurus}           & Bob Kreft & & \\
    \textit{Canis familiaris}     &  & & \\
    \textit{Dasypus novemcinctus} &  & & \\
    \textit{Equus caballus}       & \citet{Coleman.ea2010:Structuralannotationofequine} & GSM1139275 & SRR850299,  SRR850300 \\
    \textit{Loxodonta africana}   & Kurt Benirschke & & \\
    \textit{Homo sapiens}         & Karina Richani, \citet{Hughes.ea2015:Evaluatingintra-andinter-individual} & GSE66622 
                                             & SRR1850945,
                                               SRR1850946, 
                                               SRR1850951, 
                                               SRR1850952, 
                                               SRR1850953, 
                                               SRR1850954, 
                                               SRR1850957, 
                                               SRR1850958, 
                                               SRR1850965, 
                                               SRR1850966, 
                                               SRR1850975, 
                                               SRR1850976, 
                                               SRR1850983, 
                                               SRR1850984, 
                                               SRR1850987, 
                                               SRR1850988, 
                                               SRR1850991, 
                                               SRR1850992, 
                                               SRR1850993, 
                                               SRR1850994, 
                                               SRR1850995, 
                                               SRR1850996, 
                                               SRR1851003, 
                                               SRR1851004, 
                                               SRR1851011, 
                                               SRR1851012 \\
    \textit{Monodelphis domestica} & K. Smith & & \\
    \textit{Mus musculus}         & J. Gonzalez, \citet{Wang.ea2011:surveyfornovelimprinted} & GSE29690 
                                     & SRR243594,
                                       SRR243595,
                                       SRR243596,
                                       SRR243597,
                                       SRR243598,
                                       SRR243599,
                                       SRR243600,
                                       SRR243601,
                                       SRR243602,
                                       SRR243586,
                                       SRR243587,
                                       SRR243588,
                                       SRR243589,
                                       SRR243590,
                                       SRR243591,
                                       SRR243592,
                                       SRR243593\\
    \textit{Nannospalax galili}   &  & GSE68763 & SRR2016467 \\
    \textit{Ovis aries}           & \citet{Archibald.ea2010:sheepgenomereferencesequence} & ERP005642 & ERR489144, ERR489145\\
    \textit{Pan paniscus}         &  & \\
    \textit{Spalax carmeli}       &  & GSE68763 & SRR2016467 \\
    \textit{Sus scrofa}           & \citet{Ahanda.ea2012:Predictionofaltered3-} &  SRP014902 & SRR543893 \\
    \bottomrule
  \end{tabular}
  \caption{Species, experiment and species numbers used in the analyses presented in this paper}
  \label{tab:srr_numbers}
\end{table}

>>>>

\begin{table}
  \begin{tabular}{c p{1.5in} c p{2in}}
    \toprule
    Species                       & Collector & Experiment Number & Sample Number(s) \\
    \midrule
    \textit{Ateles fusciceps}     & Kurt Benirschke & & \\
    \textit{Bos taurus}           & Bob Kreft & & \\
    \textit{Canis familiaris}     & Dalen Agnew & & (Bounty Hubler) \\
    \textit{Dasypus novemcinctus} & Richard Truman & & \\
    \textit{Equus caballus}       & \citet{Coleman.ea2010:Structuralannotationofequine} & GSM1139275 & SRR850299,  SRR850300 \\
    \textit{Loxodonta africana}   & Kurt Benirschke & & \\
    \textit{Homo sapiens}         & Nandor Gabor, \citet{Hughes.ea2015:Evaluatingintra-andinter-individual} & GSE66622 
                                             & SRR1850945,
                                               SRR1850946, 
                                               SRR1850951, 
                                               SRR1850952, 
                                               SRR1850953, 
                                               SRR1850954, 
                                               SRR1850957, 
                                               SRR1850958, 
                                               SRR1850965, 
                                               SRR1850966, 
                                               SRR1850975, 
                                               SRR1850976, 
                                               SRR1850983, 
                                               SRR1850984, 
                                               SRR1850987, 
                                               SRR1850988, 
                                               SRR1850991, 
                                               SRR1850992, 
                                               SRR1850993, 
                                               SRR1850994, 
                                               SRR1850995, 
                                               SRR1850996, 
                                               SRR1851003, 
                                               SRR1851004, 
                                               SRR1851011, 
                                               SRR1851012 \\
    \textit{Monodelphis domestica} & K. Smith & & \\
    \textit{Mus musculus}         & J. Gonzalez, \citet{Wang.ea2011:surveyfornovelimprinted} & GSE29690 
                                     & SRR243594,
                                       SRR243595,
                                       SRR243596,
                                       SRR243597,
                                       SRR243598,
                                       SRR243599,
                                       SRR243600,
                                       SRR243601,
                                       SRR243602,
                                       SRR243586,
                                       SRR243587,
                                       SRR243588,
                                       SRR243589,
                                       SRR243590,
                                       SRR243591,
                                       SRR243592,
                                       SRR243593\\
    \textit{Nannospalax galili}   & Eviator Nevo & GSE68763 & SRR2016467 \\
    \textit{Ovis aries}           & \citet{Archibald.ea2010:sheepgenomereferencesequence} & ERP005642 & ERR489144, ERR489145\\
    \textit{Pan paniscus}         &  William Mintz Fields & & (Teco)\\
    \textit{Spalax carmeli}       & Eviator Nevo & GSE68763 & SRR2016467 \\
    \textit{Sus scrofa}           & \citet{Ahanda.ea2012:Predictionofaltered3-} &  SRP014902 & SRR543893 \\
    \bottomrule
  \end{tabular}
  \caption{Species, experiment and species numbers used in the analyses presented in this paper}
  \label{tab:srr_numbers}
\end{table}
